---
title: "solution"
output:
  pdf_document: default
  word_document: default
---
Begin by reading in the data.
```{r}
library(readr)
data <- read_csv("data.csv")
attach(data)
data
```
Next, let x=NumMDs, y=NumBeds. Visualize the relationship between the 2 variables using a scatterplot. 
```{r}
plot(NumBeds~NumMDs)
```
Notice that there appears to be some clustering near the origin, as well as some "fanning" at larger x-values. 

Since the scatterplot does not satisfy the conditions for linearity, we must perform transformations on one (or both) of the variables to get a better linear model.  

We start by attempting a square-root transformation on both variables. 
```{r}
plot(sqrt(NumBeds)~sqrt(NumMDs))
```
Notice that the data appear much better than before, though there are still signs of clustering near the origin. 

Let's compare our results using a log transform on both variables. 
```{r}
plot(log(NumBeds)~log(NumMDs))
```
Indeed, not only do the data appear more linear, but they also seem to be more well-dispersed. Thus, we gather that using log transforms on both variables should suffice!

To be sure, let's fit a linear model & verify that the conditions for linearity are met. Specifically, 
1. Zero-mean
2. Homoscedasticity
3. Independence
4. Normality
```{r}
plot(log(NumBeds)~log(NumMDs))
model = lm(log(NumBeds)~log(NumMDs))
abline(model)
```
We can plot a histogram of the model residuals to verify normality. 
```{r}
hist(model$residuals)
```
Indeed, the residuals appear fairly normal, with the exception of an outlier or two. Hence, we conclude that the condition for normality are met. 

Then, we check the conditions of zero-mean & constant variance by plotting the model residuals against the model’s fitted values. 
```{r}
plot(model)
```
Notice, the residuals are well dispersed about the zero-line, with no signs of clustering or grouping, nor any trends like fanning or tailing. Hence, we determine that the 2 conditions are indeed satisfied. 

Finally, we verify independence using the model's p-value. 
```{r}
summary(model)
```
At a p-value: < 2.2e-16, we can be confident the transformed variables are independent, thus concluding that all 4 conditions are satisfied!