---
title: "solution"
output: word_document
---
Read in the data.
```{r}
library(readr)
data <- read_csv("data.csv")
attach(data)
head(data)
```
Fit a model to the relevant predictors (see hw6) and print the model summary. 
```{r}
model = lm(GPA ~ HSGPA + SATV)
summary(model)
```
Also print the ANOVA table for the overall model.
```{r}
anova(model)
```
Our hypotheses tests proceeds as follows: 
  H_0: beta_i = 0, there is no relationship between a student's high school GPA / SAT verbal scores and their first year college GPA
  H_a: beta_i != 0, there is a relationship between a student's high school GPA / SAT verbal scores and their first year college GPA
  
The test-statistics, degrees of freedom, and corresponding p-values for each of the predictors are:
  HSGPA: t = 6.629, df = 1, p = 2.66e-10
  SATV: t = 3.641, df = 1, p = 0.00034

Thus, using a significance level of 0.05, we find that there's sufficient evidence to reject the null (for both cases) in favor of the alternative. We conclude that there is a relationship between a student's first year college GPA and their high school GPA / SAT verbal scores.